Apropos Replacement \newline (Initial Outline)

### 2011-12-26 paper.tex
more fixes

In this paper the limitations of the traditional implementation of
\textit{apropos} are discussed along with brief details of how those limitations
have been solved in the implementation developed as part of this project and also
what other modern implementations are available out there.
\section{Introduction}
The classical version of \textit{apropos} has been implemented by simply
indexing the keywords in the NAME section of the man pages in a plain text file
(whatis.db) [2]
and performing searches on it. The reason for this simple design was most
probably lack of computing resources in the early days. The plain text file
consisting of keywords would hardly take few hundreds of kilo bytes of disk space
and performing search on a plain text file is also not very hard.

This simplified design of \textit{apropos(1)} resulted in limited utility and
usability.The searches are limited to the keywords in the NAME section of the
 keywords. If
only a user knows the exact keywords he gets the right results otherwise most of
the times the searches are full of bogus results or a dead end. In the modern
computing world where hard problems like searching the World Wide Web have been
solved [3] to sufficient degree where most of the data is unstructured, then it
makes perfect sense that we leverage the advancement in technology to solve the
problem of an effective man page search tool, considering the fact that the man
pages consist of structured data.

@@

\subsection{Lack of support for free form queries}
The conventional \textit{apropos} is limited to the keywords used in the NAME
section
of the man pages. If the user specifies keywords relevant to the page which he
is looking but probably those keywords are not used in it's NAME section,
then \textit{apropos(1)} would not return
anything relevant. So in essence the user cannot use free form queries like
those supported by modern search applications.
\lstset{language = sh, caption={No results for free form queries}}
\begin{lstlisting}
$ apropos(1) ``add new user''
add new user: nothing appropriate

$ apropos(1) ``get process status''
get process status: nothing appropriate

$ apropos(1) ``termcap database''
termcap database: nothing appropriate

$ apropos(1) ``signal number to string''
signal number to string: nothing appropriate
\end{lstlisting}

@@

\section{Proposed Solution}
A very simple and straightforward solution is proposed to solve these problems.
The idea is to parse and index
the complete content (or at least most of the content) in the form of an
inverted index [4] and use it to build a full text search
interface. Having an index based on the complete content of the man pages solves
many of the search
related problems associated with the conventional \textit{apropos(1)} as noted
before and discussed as follows:
\begin{description}
\item[Free Form Queries] \hfill \\
The users can express their queries in more natural language form as the searches
are no longer limited to the keywords defined in the NAME section of the man
pages, the keywords used throughout the body of the page also play a role.
For example queries like \textit{``installing new software package''}
will now get results.
\end{description}
\begin{description}
\item[Basic Natural Language Processing Support] \hfill \\
When parsing the man pages and building the index, it is also possible to
pre-process the tokens extracted from the man pages to support some of the very
basic natural language processing functionalities. In this implementation the
Porter stemming algorithm [5] has been used to
reduce the individual tokens extracted from the man pages to their root words.
This enables support for more flexible searches. For example both
\textit{``Installing new packages''} and \textit{``install new package''} will
return same results.

@@

In this implementation, both word stemming and spelling correction in our implementation are used to make the search experience more smooth.
\end{description}
\begin{description}
\item[Bookkeeping of man page metadata] \hfill \\
In this implementation additional metadata related to the man pages, for example
an md5 hash, the device id, inode number and modification time
of the man page file etc. are indexed and stored so
as to support fast and hassle free updating of the index as new man pages are
installed or the old ones are modified/updated.

@@

The two main tasks that are needed to be performed are parsing of the man pages

>>>>

In this paper the limitations of the traditional implementation of
\textit{apropos} are discussed along with brief details of how those limitations
have been solved in the implementation developed as part of this project and also
what other modern implementations are available out there.
\section{Introduction}
The classical version of \textit{apropos} has been implemented by simply
indexing the keywords in the NAME section of the man pages in a plain text file
(whatis.db) [2]
and performing searches on it. The reason for this simple design was most
probably lack of computing resources in the early days. The plain text file
consisting of keywords hardly takes few hundreds of kilo bytes of disk space
and performing search on a plain text file is also not very hard.

This simplified design of \textit{apropos(1)} resulted in limited utility and
usability.The searches are limited to the keywords in the NAME section of the
 keywords. If
only a user knows the exact keywords he gets the right results otherwise most of
the times the searches are full of bogus results or a dead end. In the modern
computing world where hard problems like searching the World Wide Web have been
solved [3] to sufficient degree, then it makes perfect sense that we leverage the advancement in technology to solve the problem of an effective man page
search tool, considering the fact that the man
pages consist of structured data, making the problem somewhat less complex.

@@

\subsection{Lack of support for free form queries}
The conventional \textit{apropos} is limited to the keywords used in the NAME
section
of the man pages. If the user specifies keywords relevant to the page which he
is looking but probably those keywords are not used in the NAME section,
then \textit{apropos} would not return
anything relevant. So in essence the user cannot use free form queries like
those supported by modern search applications.
\lstset{language = sh, caption={No results for free form queries}}
\begin{lstlisting}
$ apropos ``add new user''
add new user: nothing appropriate

$ apropos ``get process status''
get process status: nothing appropriate

$ apropos ``termcap database''
termcap database: nothing appropriate

$ apropos ``signal number to string''
signal number to string: nothing appropriate
\end{lstlisting}

@@

\section{Proposed Solution}
A very simple and straightforward solution is proposed to solve these problems as
part of this project.
The idea is to parse and index
the complete content (or at least most of the content) in the form of an
inverted index [4] and use it to build a full text search
interface. Having an index based on the complete content of the man pages solves
many of the search
related problems associated with the conventional \textit{apropos(1)} as noted
before and discussed as follows:
\begin{description}
\item[Free Form Queries] \hfill \\
The users can express their queries in more natural language form as the searches
are no longer limited to the keywords defined in the NAME section of the man
pages, the keywords used throughout the body of the page also play a role.
For example queries like \textit{``installing new software package''}
will now get results.
\end{description}
\begin{description}
\item[Basic Natural Language Processing Support] \hfill \\
When parsing the man pages and building the index, it is also possible to
pre-process the tokens extracted from the man pages to support some of the very
basic natural language processing functionalities. In this implementation the
Porter stemming algorithm [5] has been used to
reduce the individual tokens extracted from the man pages to their root words.
This enables support for more flexible searches. For example both
\textit{``Installing new packages''} and \textit{``install new package''} will
return same results.

@@

In this implementation, both word stemming and spelling correction in our implementation are used to make the search experience more smooth.
\end{description}
\begin{description}
\item[Bookkeeping of man page metadata] \hfill \\
In this implementation additional metadata related to the man pages, for example
an md5 hash, the device id, inode number and modification time
of the man page files are indexed and stored so
as to support fast and hassle free update of the index as new man pages are
installed or the old ones are modified/updated.

@@

The two main tasks that are needed to be performed to implement this project are
parsing of the man pages
